Supernovae Time Profiles as a Portal to New Physics at Neutrino Telescopes

### 2024-02-03 paper/sections/model.tex
Updates from Overleaf

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from Standard Model production and two majoron hypotheses}}.
    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
    }
    \label{fig:fluxes}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
    \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
    These are the same points in the parameter space as Fig.~\ref{fig:fluxes}.
    }
    \label{fig:hits_and_likelihood}
\end{figure*}

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from Standard Model production and two majoron hypotheses}}.
    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
    In the case of the lower-mass model, the majoron can still travel relativistically, leading to a peak in the spectrum at an earlier time.
    In the case of the higher-mass model, the majoron travels subliminally, and thus, the flux peaks at later times.
    Since the dominant interaction is inverse beta decay at these energies, we expect the observed timing distribution to follow the $\bar{\nu}_{e}$
    }
    \label{fig:fluxes}
\end{figure}

@@

% \begin{figure*}
%     \centering
%     \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
%     \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
%     These are the same points in the parameter space as Fig.~\ref{fig:fluxes}.
%     }
%     \label{fig:hits_and_likelihood}
% \end{figure*}
